Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.

### 2024-03-04 docs/_tex/index.tex
maj 0403

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.},
  pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
  pdfkeywords={Drone, Remote Sensing},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{keyword}
    Drone \sep 
    Remote Sensing
\end{keyword}
\end{frontmatter}

@@

\includegraphics[width=0.5\textwidth,height=\textheight]{./Figures/Low_res/Compare_reflectance.png}

@@

\caption{\label{fig-CompareRef}Comparison of reflectance retrieved from
both low-altitude and high-altitude flights over a common area. The red
dashed line represents a linear model wheras the black dashed line
represents a 1 to 1 relationship.}

@@

In this study, a key innovation lies in the utilization of two different
altitudes (12m and 120m) for constructing the neural network model. The
lower altitude flights (8mm spatial resolution) enable precise selection
of pure pixels representing the classes used in the neural network
model. This methodology implies a consistency between the reflectance of
both altitude.

Figure~\ref{fig-CompareRef} depicts the relationship between reflectance
from a low-altitude flight and a high-altitude flight conducted over the
same area. An apparent underestimation of reflectance values is observed
in the high-altitude flight, particularly for higher values. Since both
flights were conducted over vegetation areas, the highest reflectance
values correspond to the infrared part of the spectrum. The disparity in
infrared reflectance may stem from temporal differences between the
flights, possibly resulting in a slightly drier intertidal area and
consequently higher infrared reflectance. This disparity poses an issue
for the methodology followed in the present study, relying solely on one
flight height for training. To address this issue, we employed min/max
standardized reflectance spectra as predictors for the model
(Equation~\ref{eq-std} ; \citep{Cao2017}). This approach allows us to
eliminate differences in the level of reflectance, focusing instead on
the shape of the spectra. This is a key feature in building a model that
can reliably predict vegetation across geographical sites and seasons.
It enables consistent prediction of vegetation classes across variations
in biomass and variability in light conditions \citetext{\citealp[
]{fyfe2003spatial}; \citealp[
]{COSTA2021107018}; \citealp{piaser2023impact}}.

@@

\section{Conclusion}\label{conclusion}

\renewcommand\refname{Bibliography}
  \bibliography{library.bib}

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery.},
  pdfauthor={Simon Oiry; Bede Ffinian Rowe Davies; Ana I. Sousa; Philippe Rosa; Maria Laura Zoffoli; Guillaume Brunier; Pierre Gernez; Laurent Barillé},
  pdfkeywords={Drone, Remote Sensing, Seagrass, Coastal
Ecosystems, Neural Network},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{keyword}
    Drone \sep Remote Sensing \sep Seagrass \sep Coastal
Ecosystems \sep 
    Neural Network
\end{keyword}
\end{frontmatter}

@@

\includegraphics[width=1\textwidth,height=\textheight]{index_files/figure-pdf/fig-CompareRef-1.pdf}

@@

\caption{\label{fig-CompareRef}Comparison of reflectance retrieved from
both low-altitude and high-altitude flights over a common area. The red
dashed line represents a linear model wheras the black dashed line
represents a 1 to 1 relationship. Left (A) plots RAW data and right (B)
plots standardise data.}

@@

In this study, a key innovation lies in the utilization of two different
altitudes (12m and 120m) for constructing the neural network model. The
lower altitude flights (8mm spatial resolution) enable precise selection
of pure pixels representing the classes used in the neural network
model. This methodology implies a consistency between the reflectance of
both altitude. Figure~\ref{fig-CompareRef} (A) depicts the relationship
between reflectance from a low-altitude flight and a high-altitude
flight conducted over the same area. An apparent underestimation of
reflectance values is observed in the high-altitude flight, particularly
for higher values. Since both flights were conducted over vegetation
areas, the highest reflectance values correspond to the infrared part of
the spectrum.

The disparity in infrared reflectance may stem from temporal differences
between the flights, possibly resulting in a slightly drier intertidal
area and consequently higher infrared reflectance. This disparity poses
an issue for the methodology followed in the present study, relying
solely on one flight height for training. To address this issue, we
employed min/max standardized reflectance spectra as predictors for the
model (Equation~\ref{eq-std} ; Figure~\ref{fig-CompareRef} (B) ;
\citep{Cao2017}). This approach allows us to eliminate differences in
the level of reflectance, focusing instead on the shape of the spectra.
This is a key feature in building a model that can reliably predict
vegetation across geographical sites and seasons. It enables consistent
prediction of vegetation classes across variations in biomass and
variability in light conditions \citetext{\citealp[
]{fyfe2003spatial}; \citealp[
]{COSTA2021107018}; \citealp{piaser2023impact}}.

The Figure~\ref{fig-upscaling} demonstrates that a seagrass cover
percentage of 90 \% is necessary for confident prediction of seagrass
presence. This highlights a limitation of the methodology used to
construct the training dataset for the model. The dataset was composed
exclusively of pure pixels, which has resulted in the model's reduced
confidence when faced with lower percentages of seagrass cover.
Intertidal seagrasses exhibit strong phenology, with varying pigment
composition throughout the year\citetext{\citealp[
]{bargain2013seasonal}; \citealp{legare2022remote}}. This suggests that
outside of the biomass peak of seagrasses, this model may be less
accurate. Further investigation is warranted to explore this aspect.

@@

Climate change, global warming, alien and invasive species development,
coastal erosion, sealevel rise, while further impact coastal ecosystems
in the future \citetext{\citealp{SCHIBALSKI2022101414}; \citealp[
]{holon2018predictive}; \citealp{marquet2024global}}. The demand for
meaningful and efficient monitoring methods for these habitats has
therefore never been greater \citetext{\citealp[
]{muller2018satellite}; \citealp[
]{villalobos2023remote}; \citealp{oiry2021using}}. Employing traditional
sampling methods to monitor these ecosystems is time and
resource-intensive, and the findings are often difficult to scale up.
Earth observation methods can bridge this gap and meet the needs for
monitoring coastal ecosystems. \citep{papathanasopoulou2019satellite}.
The retrieval of Essential Biodiversity Variables (EBVs) and Essential
Ocean Variables (EOVs) through satellite observations is increasingly
common, enabling comprehensive monitoring of entire ecosystems over
extended time periods \citetext{\citealp[
]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}.

\renewcommand\refname{Conclusion}
  \bibliography{library.bib}

### 2024-03-04 index.qmd
maj 0403

@@

  container-title: Earth and Space Science

@@

```{r Figure1}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: >
#|   Sites observed by drone. A: Gulf of Morbihan, B: Bourngeuf Bay, C: Ria de Aveiro Lagoon. Light green represent terrestrial areas whereas darkgreen represent intertidal areas. 
#| label: fig-map
#| fig-width: 7
#| fig-height: 7
#| out-width: "100%"

@@

::: columns
::: column
```{r Plot Reflectance_Validation 2 height}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area. The red dashed line represents a linear model wheras the black dashed line represents a 1 to 1 relationship. 
#| label: fig-CompareRef
#| fig-width: 10
#| fig-height: 10
#| out-width: "100%"

knitr::include_graphics("./Figures/Low_res/Compare_reflectance.png")
```
:::

::: column
In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model. The lower altitude flights (8mm spatial resolution) enable precise selection of pure pixels representing the classes used in the neural network model. This methodology implies a consistency between the reflectance of both altitude. @fig-CompareRef depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area. An apparent underestimation of reflectance values is observed in the high-altitude flight, particularly for higher values. Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.
:::
:::

The disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance. This disparity poses an issue for the methodology followed in the present study, relying solely on one flight height for training. To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; [@Cao2017]). This approach allows us to eliminate differences in the level of reflectance, focusing instead on the shape of the spectra. This is a key feature in building a model that can reliably predict vegetation across geographical sites and seasons. It enables consistent prediction of vegetation classes across variations in biomass and variability in light conditions [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].

The @fig-upscaling demonstrates that a seagrass cover percentage of `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % is necessary for confident prediction of seagrass presence. This highlights a limitation of the methodology used to construct the training dataset for the model. The dataset was composed exclusively of pure pixels, which has resulted in the model's reduced confidence when faced with lower percentages of seagrass cover. This implies that outside of the biomass peak of seagrass this model should be less accurate. This needs to be futher investigated.

@@

>>>>

  - Seagrass
  - Coastal Ecosystems
  - Neural Network 

@@

  container-title: Remote Sensing of Environment

@@

```{r Figure1}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: >
#|   Sites observed by drone. A: Gulf of Morbihan, B: Bourngeuf Bay, C: Ria de Aveiro Lagoon. Light green represent terrestrial areas whereas darkgreen represent intertidal areas. 
#| label: fig-map
#| fig-width: 10
#| fig-height: 10
#| out-width: "100%"

@@

```{r}
#| cache: false
#| echo: false
#| warning: false
#| fig-cap: Comparison of reflectance retrieved from both low-altitude and high-altitude flights over a common area. The red dashed line represents a linear model wheras the black dashed line represents a 1 to 1 relationship. Left (A) plots RAW data and right (B) plots standardise data. 
#| label: fig-CompareRef
#| fig-width: 10
#| fig-height: 5
#| out-width: "100%"

RAW <- ggplot()+
  geom_spatraster_rgb(data = rast("./Figures/Low_res/Compare_reflectance.png"))+
  coord_equal()+
  geom_label(aes(x = 300,y= 1200, label = "A") ,size = 10)+
    theme_void()+
  theme(axis.text = element_blank(), 
        axis.title = element_blank(), 
        axis.ticks = element_blank(), 
        axis.ticks.length = unit(0, "pt"),
        panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "pt"))

STD <- ggplot()+
  geom_spatraster_rgb(data = rast("./Figures/Low_res/Compare_reflectance_std.png"))+
  coord_equal()+
  geom_label(aes(x = 300,y= 1200, label = "B") ,size = 10)+
    theme_void()+
  theme(axis.text = element_blank(), 
        axis.title = element_blank(), 
        axis.ticks = element_blank(), 
        axis.ticks.length = unit(0, "pt"),
        panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "pt"))

RAW+STD

In this study, a key innovation lies in the utilization of two different altitudes (12m and 120m) for constructing the neural network model. The lower altitude flights (8mm spatial resolution) enable precise selection of pure pixels representing the classes used in the neural network model. This methodology implies a consistency between the reflectance of both altitude. @fig-CompareRef (A) depicts the relationship between reflectance from a low-altitude flight and a high-altitude flight conducted over the same area. An apparent underestimation of reflectance values is observed in the high-altitude flight, particularly for higher values. Since both flights were conducted over vegetation areas, the highest reflectance values correspond to the infrared part of the spectrum.

The disparity in infrared reflectance may stem from temporal differences between the flights, possibly resulting in a slightly drier intertidal area and consequently higher infrared reflectance. This disparity poses an issue for the methodology followed in the present study, relying solely on one flight height for training. To address this issue, we employed min/max standardized reflectance spectra as predictors for the model (@eq-std ; @fig-CompareRef (B) ; [@Cao2017]). This approach allows us to eliminate differences in the level of reflectance, focusing instead on the shape of the spectra. This is a key feature in building a model that can reliably predict vegetation across geographical sites and seasons. It enables consistent prediction of vegetation classes across variations in biomass and variability in light conditions [@fyfe2003spatial ; @COSTA2021107018 ; @piaser2023impact].

The @fig-upscaling demonstrates that a seagrass cover percentage of `r round((lm_magno$coefficients[[2]]*85+lm_magno$coefficients[[1]])*100,0)` % is necessary for confident prediction of seagrass presence. This highlights a limitation of the methodology used to construct the training dataset for the model. The dataset was composed exclusively of pure pixels, which has resulted in the model's reduced confidence when faced with lower percentages of seagrass cover. Intertidal seagrasses exhibit strong phenology, with varying pigment composition throughout the year[@bargain2013seasonal ; @legare2022remote]. This suggests that outside of the biomass peak of seagrasses, this model may be less accurate. Further investigation is warranted to explore this aspect.

@@

Climate change, global warming, alien and invasive species development, coastal erosion, sealevel rise, while further impact coastal ecosystems in the future [@SCHIBALSKI2022101414; @holon2018predictive ; @marquet2024global]. The demand for meaningful and efficient monitoring methods for these habitats has therefore never been greater [@muller2018satellite ; @villalobos2023remote ; @oiry2021using]. Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to scale up. Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems. [@papathanasopoulou2019satellite]. The retrieval of Essential Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs) through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020].
